---
output:
  pdf_document: default
  html_document: default
---
```{R}
#import libraries
library(cobalt)
library(WeightIt)
library(lmtest)
library(sandwich)
```


```{R}
farms_df <- read.csv("farms.csv")
head(farms_df)
```


```{R}
#balance plot for the average age
bal.plot(
  x = cover_10 ~ age_avg,
  data = farms_df,
  var.name = "age_avg"
)
```

```{R}
#balance plot for the different regions
bal.plot(
  x = cover_10 ~ region,
  data = farms_df,
  var.name = "region"
)
```

```{R}
#balance table to show SMD (Standardized Mean Differences) and Variance Ratios for all predictor variables according to the treatment group
bal.tab(
  x = cover_10 ~ age_avg + region,
  data = farms_df,
  binary = "std",
  disp.v.ratio = TRUE
)
```

- The SMDs are outside of the recommended -0.1 and 0.1 range.
- The variance ratio for age_avg is within the recommended range of 0.5 - 2.0

```{r}
# Calculate IPTW weights with initial propensity score model
farm_iptw <- weightit(
  cover_10 ~ region + total_avg + insurance_avg + fertilizer_per_area,
  data = farms_df,
  estimand = "ATE",
  method = "ps"
)
```

```{r}
#plot love plot to evaluate SMD for farm_iptw before and after weighting
love.plot(
  x = farm_iptw,
  binary = "std",
  thresholds = c(m = 0.1)
)
```
Close after weighting but needs refinement.

```{r}
#create new propensity score model with new values
farm_iptw2 <- weightit(
  cover_10 ~ region + total_avg + insurance_avg + age_avg + easement_p + experience_avg + conservation_till_avg,
  data = farms_df,
  estimand = "ATE",
  method = "ps"
)
```

```{r}
#plot love plot showing SMD of new propensity score model
love.plot(
  x = farm_iptw2,
  binary = "std",
  thresholds = c(m = 0.1)
)
```
The SMD values are closer to zero than before, showing that this model is an improvement.

```{r}
#plot bal plot to show propensity scores before and after weighting
bal.plot(
  x = farm_iptw2,
  var.name = "prop.score",
  which = "both"
)
```

```{r}
#fit a regression model for total crop yield as the outcome, cover crop useage as the treatment and other variables from the propensity score model as other predictors
yield_mod <- glm(
  total_yield ~ cover_10 + region + total_avg + insurance_avg + age_avg + easement_p + experience_avg + conservation_till_avg,
  data = farms_df,
  weights = farm_iptw2$weights
)
```

With the regression model fitted, we now need robust standard errors

```{r}
#estimate regression parameters for the weighted regression model
coeftest(
  yield_mod,
  vcov. = vcovHC
)
```

The estimate of the ATE (Average Treatment Effect) for cover_10 (at least 10% of farms have cover crops) on total yield is 3.58.
Meaning that for counties that have at least 10% of farms with cover crops, the yield increases by 3.58 units (bushels per acre).
